### 2016-03-08 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated hose stream report drawings

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
	\label{fig:east_dimensioned_plan}
\end{figure}

@@

Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there is no statistically significant difference in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counter clockwise direction for any of three hose streams tested.

% ===========
% = Summary =
% ===========
\chapter{Summary}
\label{chap:summary}
**** Will briefly restate purpose of experiments, objectives, setup, results etc. ****
List of main findings:
\begin{enumerate}
\item More air movement with NF and WF than SS
\item More air movement when the hose stream was applied in a pattern that involved moving the nozzle compared to keeping the stream in a fixed position.
\item No noticeable difference between rotating hose CW or CCW
\end{enumerate}

@@

In addition to the monitor experiments, three different experiments were conducted using a handline to study the impact of different stream and application pattern combinations on air movement within a structure.

% ===============
% = FUTURE WORK =
% ===============
\chapter{Future Work}
\label{chap:Future_Work}
Need to determine if air movement caused by hose streams has significant impact on flow path/ventilation and fire development in an involved structure. May want to compare air velocities to movements caused by PPV fans.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
	\caption{Average velocity through the interior doorway during Test 33 for three hose stream patterns.}
	\label{fig:Test_33_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
	\caption{Average velocity through stairwell door during Test 34 for three hose stream patterns.}
	\label{fig:Test_34_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout. Interior dimensions are symmetric across horizontal and vertical centerlines.}
	\label{fig:east_dimensioned_plan}
\end{figure}

@@

Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counter clockwise direction for any of three hose streams tested.

% ===========
% = Summary =
% ===========
\chapter{Summary}
\label{chap:summary}

@@

In addition to the monitor experiments, three different experiments were conducted using a handline to study the impact of different stream and application pattern combinations on air movement within a structure. Similar to the monitor experiments, the average air velocity through the interior doorway of a structure with a fully established flow path was greater for the wide fog and narrow fog streams than the straight stream. In fact, it was discovered that a straight stream only caused significant air movement through the interior doorway when it was applied in a moving pattern. Additionally, throughout all handline experiments, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counter clockwise application patterns.

Overall, the water flow experiments discussed in this report reveal that hose streams can affect air movement within a structure. The type of hose stream used and manner in which it is applied dictates the extent to which a stream impacts the ventilation of a structure. These experiments have shown there is a potential for hose streams to affect air flows within a structure during fire scenarios. To better quantify the impact of air flows from hose streams on the fire environment, additional fire experiments need to be conducted.

@@

\begin{figure}[!ht]
	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
	\caption{Average velocity through the interior doorway during Test 33 for three hose stream patterns.}
	\label{fig:Test_33_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
	\caption{Average velocity through stairwell door during Test 34 for three hose stream patterns.}
	\label{fig:Test_34_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier
